For Induction-Induction, Induction is Enough

### 2019-11-12 paper/paper.tex
update notations and abbreviations

We define $\sigma^\uparrow$ as $(\sigma\circ\p,\q)$.
We also abbreviate non-dependent $\Pi$ functions by writing $\Pi\,a\,(B[\p])$ as $a\Ra B$.

We can also recover de Bruijn indices by having $n := \q[\p^n]$, where $\p^n$ is
$\p$ composed with itself $n$ times. However, for informal examples we instead
use a nameful notation, where we introduce names in context extension and in the
$\Pi$ function domain, for example as $\boldsymbol{\cdot}\,\ext\,A : \U\,\ext\,a :
\El\,A$ in a signature for pointed sets.

>>>>

We define $\wk : \Sub\,(\Gamma\ext A)\ra \Gamma$ as $\pi_1\,\id$.
We can recover de Bruijn indices by having $0= \pi_2 \,\id$ and $n+1 = n[\wk]$.
However, for informal examples we instead
use a nameful notation, where we introduce names in context extension and in the
$\Pi$ function domain, for example as $\boldsymbol{\cdot}\,\ext\,A : \U\,\ext\,a :
\El\,A$ in a signature for pointed sets.

We define $\sigma^\uparrow$ as $(\sigma\circ\wk,0)$.
We also abbreviate non-dependent $\Pi$ functions by writing $\Pi\,a\,(B[\wk])$ as $a\Ra B$.
